\huge A Usability Evaluation of Tor Launcher

### 2017-03-14 pets2017-paper/pets2017-paper.tex

\subsection{Procedure} 
We ran the experiment in a meeting room at UC Berkeley. The room had a desk and chair, where a monitor, keyboard, and a Windows computer were set up. On a clean computer, we downloaded and installed Tor Browser 5.0.3 for testing, Chrome, Firefox, and Internet Explorer so that a participant could browse the Internet in another browser of their choice, and VLC~\cite{vlc} to record the screen during the experiment. Before each participant, we ran a script on the computer that set up one of the three simulated environments (E1, E2, or E3) and started recording the computer screen.

@@

\subsection{Procedure}
We ran our experiment at the Xlab~\cite{xlab}, an experimental social science laboratory. The room had 36 workstations with identical Windows~7 laptops. Workstation partitions discouraged participants from looking at other screens. We automatically reverted the computers to the same image at the beginning of each session. Before each session, we ran a script that downloaded the necessary software (Firefox, Chrome, IE, and VLC, and Tor Browser 5.0.3 or a modified version of Tor 5.0.3 with our proposed UI changes), set up one of the three simulated environments (E1, E2, or E3), and started the computer screen recording. We instrumented Tor Browser to log user interactions. We manually assigned each computer to one of the six interface--environment combinations in a way that evenly distributed experimental conditions throughout the room.

@@

\section {Acknowledgments}
We would like to thank the peer reviewers, especially our shepherd Jens Grossklas, for giving us valuable feedback on this paper. Tor Project employees Georg Koppen, Mike Perry, and Isabela Bagueros provided valuable insights about the history of Tor launcher and internal constraints. This work was done in collaboration with Xlab (Experimental Social Science Laboratory)~\cite{Xlab}, SCRUB (secure computing research for users' benefit)~\cite{scrub}, and BLUES (Berkeley laboratory for usable and experimental security)~\cite{blues} laboratories, with funding from Intel and the National Science Foundation.

>>>>

\subsection{Procedure} 
We ran the experiment in a meeting room at UC Berkeley. The room had a desk and chair, where a monitor, keyboard, and a Windows computer were set up. On a clean computer, we downloaded and installed Tor Browser 5.0.3 for testing, Chrome, Firefox, and Internet Explorer so that participants could browse the Internet in another browser of their choice, and VLC media player~\cite{vlc} to record the screen during the experiment. Prior to each participant, we ran a script on the computer that set up one of the three simulated environments (E1, E2, or E3) and started recording the computer screen.

@@

\subsection{Procedure}
We ran our experiment at the Xlab~\cite{xlab}, an experimental social science laboratory. The room had 36 workstations with identical Windows~7 laptops. Workstation partitions discouraged participants from looking at other screens. We automatically reverted the computers to the same image at the beginning of each session. Before each session, we ran a script that downloaded the necessary software (Firefox, Chrome, Internet Explorer, VLC media player, and Tor Browser 5.0.3 with or without our proposed UI changes), set up one of the three simulated environments (E1, E2, or E3), and started the computer screen recording. We instrumented Tor Browser to log user interactions. We manually assigned each computer to one of the six interface--environment combinations in a way that evenly distributed experimental conditions throughout the room.

@@

\section {Acknowledgments}
We would like to thank the peer reviewers, especially our shepherd Jens Grossklas, for giving us valuable feedback on this paper. Tor Project employees Georg Koppen, Mike Perry, and Isabela Bagueros provided valuable insights about the history of Tor launcher and internal constraints. This work was done in collaboration with Xlab (Experimental Social Science Laboratory)~\cite{xlab}, SCRUB (secure computing research for users' benefit)~\cite{scrub}, and BLUES (Berkeley laboratory for usable and experimental security)~\cite{blues} laboratories, with support from
Intel, the National Science Foundation,
the Open Technology Fund through the Freedom2Connect Foundation, and from
the US Department of State, Bureau of Democracy, Human Rights and Labor.
